### 2019-07-08 monograph/thesis/chapters/beautifiers.tex
Added new references to references.bib and rewrapped lines with
full semantic line wrapping.
Added presentation note to draft_for_implementation.tex and
split beautifiers.tex big paragraphs.
Moved computer assisted programming section as a subsection
to the end of the first section.
Translated first citation on beautifiers.tex

\advisor{}{%
    \section{\lang{Computer Assisted Programming}{Programação auxiliada}}

@@

\lang{%
    A robust Code Beautifier can get a lot more complicated just with the basic
    definitions of formatting (\nameref{source_code_beautifiers})
    applied over each language own characteristics
    as for example:
    \begin{enumerate}[nosep,nolistsep]
        \item
            Add spaces before if\s name as in `if(var)' versus `if (var)'
        \item
            Add spaces inside if\s as in `if(var)' versus `if( var )'
        \item
            Add spaces before for\s name as in `for(var)' versus `for (var)'
        \item
            Add spaces inside for\s as in `for(var)' versus `for( var )'
    \end{enumerate}
}{%
    Conhecido como ``pretty~=printing'' ou
    embelezadores\footnote{Do inglês \textit{Beautifiers}} \cite{prettyPrintingForSoftware},
    uma ferramenta de formatação pode ser complicada de se utilizar,
    somente com um conjunto básico de definições.
    Por exemplo,
    para permitir um melhor controle do usuário,
    a ferramenta de formatação pode permitir que exista uma configuração específica para cada aspecto da linguagem.
    Uma possível implementação para tal ajuste fino,
    pode ser uma configuração específica como por exemplo a entrada booleana ``\textit{use\_spaces\_after\_if}'',
    em um arquivo de configuração para definir caso deva~=se ou
    não ser adicionados espaços antes de cada ``if'' ao fazer a formatação da linguagem,
    por exemplo,
    ``if (var)'' ao contrário de ``if(var)''.
}

@@

\lang{%
    The problem about is, even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code
    formatter tool, which will be certainly
    limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.
}{%
    O problema é,
    mesmo que se passe por todas essas configurações,
    realizando os ajustes de preferência do usuário,
    isso levará um bom tempo.
    Infelizmente,
    você ainda está apenas configurando uma e
    talvez algumas linguagens fortemente relacionadas,
    dependendo do suporte que a ferramenta oferece.
    No caso da ferramenta \textit{Uncrustify},
    serão configurados as linguagens \textit{C},
    \textit{C++}, \textit{Java}, \textit{Pawn}\advisor{.}{,
    etc.} Para todos os outras linguagens,
    você ainda precisará encontrar outra ferramenta de formatação,
    que será certamente mais limitada no que ela pode customizar \cite{eclisePeriodSettings},
    uma vez que \textit{Uncrustify} já é uma das mais completas.
    Além disso,
    ainda precisa~=se configurar todas as novas opções já configuradas.
    Outra forte desvantagem do arquivo de configurações do \textit{Uncrustify} segue na dificuldade de entender e
    visualizar o que está sendo configurado.
    Algumas opções são claras e
    fáceis de se entender,
    já outras,
    não consegue~=se ter a mínima ideia do que elas estão fazendo e
    qual será o seu resultado final.
}

@@

@@

\url{https://www.python.org/dev/peps/pep-0008/#should-a-line-break-before-or-after-a-binary-operator}

For now could not find any strong evidence or correlation about code
comprehension and source code beautifying \cite{improvingCodeReadability},
except perhaps for team annoyance:

\begin{citacao}
% \setlength{\itemindent}{5pt}
One of absolute worst, worst methods of teamicide for software developers is to engage
in these kinds of passive-aggressive formatting wars. I know because I've been there.
They destroy peer relationships, and depending on the type of formatting, can also damage
your ability to effectively compare revisions in source control, which is really scary.
I can't even imagine how bad it would get if the lead was guilty of this behavior. That's
leading by example, all right. Bad example. \cite{Atwood}
\end{citacao}

On \citeonline{improvingCodeReadability} was analyzed the level of program
comprehension which can be gained by the indentation and was constated that
the indentation levels of 2 and 4 spaces proved to have the best
comprehension levels again other levels.

\begin{citacao}
So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
trivial issues of code layout is actually justified. Within reason of course -- when done
openly, in a fair and concensus building way, and without stabbing your teammates in the
face along the way. \cite{Atwood}
\end{citacao}

@@

If found on the project root folder,
a folder named `.object-beauty',
it will be used to store the automatically generated configurations based on the current configuration\s rules.
Such thing,
cannot be easily implemented because of the various complexities which can be introduced into the formatting rules.
For example,
the if configurations rules are simple and limited to just changing simple aspects of the formatting,
then the configuration generation will also be simple,
because there are only a few aspects to analyze.
However,
as the formatting rules grow up,
their complexity equally proportionally grows,
due the increased count of possibilities to analyze when combined together.

@@

With this ObjectBeautifier,
we can edit XML files like YAML files,
because the when we load the XML,
we create a copy (the YAML version of the XML) on the `.object-beauty` folder which is edited by Sublime Text,
and let the XML on its original place.
Then when we save our YAML copy,
we translate it to the XML original copy.
Similarly,
for a C language code,
it would be like to change some bit on the compiled binary code and have the change reflected on the original C source code.
\url{https://github.com/Microsoft/XmlNotepad}

>>>>

@@

\lang{%
    A robust Code Beautifier can get a lot more complicated just with the basic
    definitions of formatting (\nameref{source_code_beautifiers})
    applied over each language own characteristics
    as for example:
    \begin{enumerate}[nosep,nolistsep]
        \item
            Add spaces before if\s name as in `if(var)' versus `if (var)'
        \item
            Add spaces inside if\s as in `if(var)' versus `if( var )'
        \item
            Add spaces before for\s name as in `for(var)' versus `for (var)'
        \item
            Add spaces inside for\s as in `for(var)' versus `for( var )'
    \end{enumerate}
}{%
    Conhecido como ``pretty~=printing'' ou
    embelezadores\footnote{Do inglês \textit{Beautifiers}} \cite{prettyPrintingForSoftware},
    uma ferramenta de formatação pode ser complicada de se utilizar,
    somente com um conjunto básico de definições.
    Por exemplo,
    para permitir um melhor controle do usuário,
    a ferramenta de formatação pode permitir que exista uma configuração específica para cada aspecto da linguagem.

    Uma possível implementação para tal ajuste fino,
    pode ser uma configuração específica como por exemplo a entrada booleana ``\textit{use\_spaces\_after\_if}'',
    em um arquivo de configuração para definir caso deva~=se ou
    não ser adicionados espaços antes de cada ``if'' ao fazer a formatação da linguagem,
    por exemplo,
    ``if (var)'' ao contrário de ``if(var)''.
}

@@

\lang{%
    The problem about is, even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code
    formatter tool, which will be certainly
    limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.
}{%
    O problema é,
    mesmo que se passe por todas essas configurações,
    realizando os ajustes de preferência do usuário,
    isso levará um bom tempo.
    Infelizmente,
    você ainda está apenas configurando uma e
    talvez algumas linguagens fortemente relacionadas,
    dependendo do suporte que a ferramenta oferece.

    No caso da ferramenta \textit{Uncrustify},
    serão configurados as linguagens \textit{C},
    \textit{C++}, \textit{Java}, \textit{Pawn}\advisor{.}{,
    etc.} Para todos os outras linguagens,
    você ainda precisará encontrar outra ferramenta de formatação,
    que será certamente mais limitada no que ela pode customizar \cite{eclisePeriodSettings},
    uma vez que \textit{Uncrustify} já é uma das mais completas.

    Além disso,
    ainda precisa~=se configurar todas as novas opções já configuradas.
    Outra forte desvantagem do arquivo de configurações do \textit{Uncrustify} segue na dificuldade de entender e
    visualizar o que está sendo configurado.

    Algumas opções são claras e
    fáceis de se entender,
    já outras,
    não consegue~=se ter a mínima ideia do que elas estão fazendo e
    qual será o seu resultado final.
    Por exemplo,
    você consegue claramente entender o que a última regra do Código \ref{lst:uncrustifySettingSample} significa?
}

@@

\advisor{}{%
    \subsection{\lang{Computer Assisted Programming}{Programação auxiliada}}

@@

\lang{%
    For now could not find any strong evidence or correlation about code
    comprehension and source code beautifying \cite{improvingCodeReadability},
    except perhaps for team annoyance:
}{%
    Não pôde~=se encontrar nenhuma forte evidência ou
    relação sobre a compreensão de códigos~=fonte e
    formatadores de código.
    Somente indícios de que certas características combinadas podem melhorar ou
    facilitar a tarefa de programar \cite{pep8operatorsBlankLine}.
}%
\begin{citacao}
    % \setlength{\itemindent}{5pt}
    Um dos melhores métodos de destruição de equipes de desenvolvedores de software,
    é engajar~=se em guerras de formatação passiva~=agressiva.
    Eles destroem os relacionamentos entre colegas,
    e dependendo do tipo de formatação feita,
    também podem prejudicar a capacidade de comparar efetivamente as revisões no sistema de controle de versão,
    o que é realmente assustador.
    Não pode~=se nem imaginar o quão ruim seria caso a liderança das equipes fosse a culpada por esse comportamento.
    Isso é liderar por exemplo.
    Por mau exemplo.
    \cite[tradução nossa]{deathToTheSpaceInfidels}\footnote{
    \englishword{%
    One of absolute worst,
    worst methods of teamicide for software developers is to engage in these kinds of passive~=aggressive formatting wars.
    I know because I've been there.
    They destroy peer relationships,
    and depending on the type of formatting,
    can also damage your ability to effectively compare revisions in source control,
    which is really scary.
    I can't even imagine how bad it would get if the lead was guilty of this behavior.
    That's leading by example,
    all right.
    Bad example.
    }}.
\end{citacao}

\lang{%
    On \citeonline{improvingCodeReadability} was analyzed the level of program comprehension which can be gained by the indentation and
    was constated that the indentation levels of 2 and
    4 spaces proved to have the best comprehension levels again other levels.
}{%

}
\begin{citacao}
So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
trivial issues of code layout is actually justified. Within reason of course -- when done
openly, in a fair and concensus building way, and without stabbing your teammates in the
face along the way. \cite{deathToTheSpaceInfidels}
\end{citacao}

@@

If found on the project root folder,
a folder named `.object~=beauty',
it will be used to store the automatically generated configurations based on the current configuration\s rules.
Such thing,
cannot be easily implemented because of the various complexities which can be introduced into the formatting rules.
For example,
the if configurations rules are simple and limited to just changing simple aspects of the formatting,
then the configuration generation will also be simple,
because there are only a few aspects to analyze.
However,
as the formatting rules grow up,
their complexity equally proportionally grows,
due the increased count of possibilities to analyze when combined together.

@@

With this ObjectBeautifier,
we can edit XML files like YAML files,
because the when we load the XML,
we create a copy (the YAML version of the XML) on the `.object~=beauty` folder which is edited by Sublime Text,
and let the XML on its original place.
Then when we save our YAML copy,
we translate it to the XML original copy.
Similarly,
for a C language code,
it would be like to change some bit on the compiled binary code and have the change reflected on the original C source code.
\url{https://github.com/Microsoft/XmlNotepad}

### 2019-07-08 monograph/thesis/chapters/introduction.tex
Translated first citation on beautifiers.tex

\lang{%
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain\hyp{}text' mode. Since for code sharing, it is vital for you
    to use a versioning control system\footnote{\url{http://www.codeservedcold.com/version-control-importance/}}
    which enable project manager\s and
    programmers themselves, take control of their code changes
    \cite{redesignOfGit}. It does allow to easily perform the tracking of code
    changes \cite{gettingProductive} and
    allow you to better understand what each programmer is doing
    every time he formalizes a change in the code through a `commit', as in
    `git' systems for example \cite{usingSourceControl}.
}{%
    Indo além de como programadores leem código enquanto estão escrevendo ele,
    também tem que se preocupar como o código será salvo no sistema de arquivos,
    em seu formato de texto simples.
    Já que para compartilhar código e
    trabalhar em times de forma eficiente,
    é essencial utilizar um sistema de versionamento \cite{whyVersionControlIsCritical}.

@@

\begin{citacao}
    Há duas razões principais para impor um formato de código único em um projeto.
    A primeira razão tem a ver com o controle de versão:
    quando todo mundo formata o código de forma idêntica,
    todas as alterações nos arquivos têm a garantia de terem algum significado.
    Nada mais de coisas como adicionar ou
    remover um espaço aleatoriamente,
    muito menos formatar um arquivo inteiro como um ``efeito colateral'' de alterar apenas uma linha ou
    duas \cite[tradução nossa]{Geukens}\footnote{\englishword{I'd say there are two main reasons to enforce a single code format in a project.
    First has to do with version control:
    with everybody formatting the code identically,
    all changes in the files are guaranteed to be meaningful.
    No more just adding or
    removing a space here or
    there,
    let alone reformatting an entire file as a ``side effect'' of actually changing just a line or
    two.
    }}.
\end{citacao}

@@

\advisor{}{%
    \lang{%
        Talking about the last ideia pointed out, we could also think about an
        approach to creating a new version control system which focuses only on
        significant changes to the code, while reviewing code changes. However, this
        approach could not be ideal, as for example, it would allow programmers to
        start tedious wars of unproductive code adjustments. For example, imagine
        how it would be for your every day and have to go through your code
        re\hyp{}adding new lines before each one of your beloved if\s, just because some
        night shift programmer\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
        had just removed them?
    }{%
        Poderia~=se também pensar em uma abordagem para criar um novo sistema de controle de versão,
        que foca apenas mudanças significativas no código enquanto faz~=se a revisão das mudanças no código.
        No entanto,
        essa abordagem poderia não ser ideal,
        pois, por exemplo,
        permitiria que os programadores iniciassem guerras tediosas de ajustes de código improdutivos.
        Por exemplo,
        imagine como seria se todo os dias você tivesse que passar pelo código re~=adicionando novas linhas antes de cada um dos seus amados if\s,
        só porque algum programador do turno da noite\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}} tinha acabado de removê-los?
    }
}

>>>>

\lang{%
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain\hyp{}text' mode. Since for code sharing, it is vital for you
    to use a versioning control system \cite{whyVersionControlIsCritical} which enable project manager\s and
    programmers themselves, take control of their code changes
    \cite{redesignOfGit}. It does allow to easily perform the tracking of code
    changes \cite{gettingProductive} and
    allow you to better understand what each programmer is doing
    every time he formalizes a change in the code through a `commit', as in
    `git' systems for example \cite{usingSourceControl}.
}{%
    Indo além de como programadores leem código enquanto estão escrevendo ele,
    também tem que se preocupar como o código será salvo no sistema de arquivos,
    em seu formato de texto simples.
    Já que para compartilhar código e
    trabalhar em times de forma eficiente,
    é essencial utilizar um sistema de versionamento \cite{whyVersionControlIsCritical}.

@@

\begin{citacao}
    Há duas razões principais para impor um formato de código único em um projeto.
    A primeira razão tem a ver com o controle de versão:
    quando todo mundo formata o código de forma idêntica,
    todas as alterações nos arquivos têm a garantia de terem algum significado.
    Nada mais de coisas como adicionar ou
    remover um espaço aleatoriamente,
    muito menos formatar um arquivo inteiro como um ``efeito colateral'' de alterar apenas uma linha ou
    duas \cite[tradução nossa]{Geukens}\footnote{
    \englishword{%
    I'd say there are two main reasons to enforce a single code format in a project.
    First has to do with version control:
    with everybody formatting the code identically,
    all changes in the files are guaranteed to be meaningful.
    No more just adding or
    removing a space here or
    there,
    let alone reformatting an entire file as a ``side effect'' of actually changing just a line or
    two.
    }}.
\end{citacao}

@@

\advisor{}{%
    \lang{%
        Talking about the last ideia pointed out, we could also think about an
        approach to creating a new version control system which focuses only on
        significant changes to the code, while reviewing code changes. However, this
        approach could not be ideal, as for example, it would allow programmers to
        start tedious wars of unproductive code adjustments. For example, imagine
        how it would be for your every day and have to go through your code
        re\hyp{}adding new lines before each one of your beloved if\s, just because some
        night shift programmer had just removed them \cite{whoWroteThisCrap}?
    }{%
        Poderia~=se também pensar em uma abordagem para criar um novo sistema de controle de versão,
        que foca apenas mudanças significativas no código enquanto faz~=se a revisão das mudanças no código.
        No entanto,
        essa abordagem poderia não ser ideal,
        pois, por exemplo,
        permitiria que os programadores iniciassem guerras tediosas de ajustes de código improdutivos.
        Por exemplo,
        imagine como seria se todo os dias você tivesse que passar pelo código re~=adicionando novas linhas antes de cada um dos seus amados if\s,
        só porque algum programador do turno da noite tinha acabado de removê-los \cite{whoWroteThisCrap}?
    }
}
